Books and Babies: An Analysis of the Relationship between Female Literacy Rate and Fertility Rate in South Asia (2000-2020)

### 2024-04-18 paper/paper.qmd
update paper.qmd

---
title: "Books and Babies: An Analysis of the Relationship between Female Literacy Rate and Fertility Rate in South Asia (2000-2020)"
author: "Jagpreet Singh"
thanks: "Code and data are available at: https://github.com/Jagpreet5ingh/female_fertility_rate_south_asia.git"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
date-format: long
bibliography: references.bib
execute: 
  echo: false
format: pdf
fig-pos: "H"
abstract: This paper utilizes data from the World Bank’s Gender Statistics database to examine the relationship between the adult female literacy rate (% of females ages 15 and above) and fertility rate (total births per woman) in South Asia between 2000-2020. The analysis revealed a negative correlation between the two variables, indicating that as the literacy rate increased, the fertility rate decreased. These findings matter as they highlight the importance of investing in female education and empowerment to manage population growth and promote sustainable development. The insights can guide policymakers make decisions on education initiatives and reproductive health programs to further enhance socioeconomic progress in the region.
---

```{r}
knitr::opts_chunk$set(echo = FALSE, results ="hide", message = FALSE, warning = FALSE)
```
```{r}
#| include: false
#| warning: false
#| message: false

@@

analysis_data <- read_csv(here::here("data/analysis_data/cleaned_data_south_asia_2000_2020.csv"))

@@

## Data Source {#sec-variables-of-interest}

@@

```{r}
#| label: fig-3
#| fig-cap: "The model shows the relationship between Female Literacy Rate and Fertility Rate in South Asia (2000-2020)"
#| echo: false
#| warning: false

library(ggplot2)

analysis_data %>%
  ggplot(aes(x = `female_literacy_rate`, y = `fertility_rate_total`)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black", linetype = "solid") +
  labs(x = "Literacy Rate, Adult Females (% of females ages 15 and above)", y = "Fertility Rate, Total (births per woman)") +
  theme_classic()

>>>>

---
title: "Books and Babies: An Analysis of the Relationship between Female Literacy Rate and Fertility Rate in South Asia (2000-2020)"
author: "Jagpreet Singh"
thanks: "Code and data are available at: https://github.com/Jagpreet5ingh/female_fertility_rate_south_asia.git"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
date-format: long
bibliography: references.bib
execute: 
  echo: false
format: pdf
fig-pos: "H"
abstract: This paper utilizes data from the World Bank’s Gender Statistics database to examine the relationship between the adult female literacy rate (% of females ages 15 and above) and fertility rate (total births per woman) in South Asia between 2000-2020. The analysis revealed a negative correlation between the two variables, indicating that as the literacy rate increased, the fertility rate decreased. These findings matter as they highlight the importance of investing in female education and empowerment to manage population growth and promote sustainable development. The insights can guide policymakers make decisions on education initiatives and reproductive health programs to further enhance socioeconomic progress in the region.
---
```{r}
knitr::opts_chunk$set(echo = FALSE, results ="hide", message = FALSE, warning = FALSE)
```
```{r}
#| include: false
#| warning: false
#| message: false

@@

analysis_data <- read.csv(here::here("data/analysis_data/cleaned_data_south_asia_2000_2020.csv"))

@@

```{r, results='asis'}
#| echo: false
#| warning: false
#| label: tbl-data
#| tbl-cap: "A summary table of cleaned data"

library(knitr)

kable(analysis_data)

```
## Data Source {#sec-variables-of-interest}

@@

```{r}
#| label: fig-3
#| fig-cap: "The model shows the relationship between Female Literacy Rate and Fertility Rate in South Asia (2000-2020)"
#| echo: false
#| warning: false
library(ggplot2)

analysis_data %>%
  ggplot(aes(x = `female_literacy_rate`, y = `fertility_rate_total`)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black", linetype = "solid") +
  labs(x = "Literacy Rate, Adult Females (% of females ages 15 and above)", y = "Fertility Rate, Total (births per woman)") +
  theme_classic()
```
